---
title: "Stats 506, F18, Problem Set 3"
author: "Chen Xie, chenxie@umich.edu"
date: "`r format.Date(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Question 1


### Part a

```{r q1_source, message = FALSE}
source('./ps3_q1.R')
```

The percent of homes have stucco construction as the major outside wall material within each division is shown in the table 1 and figure 1 below.


```{r q1a_table1}
cap = '*Proportion of homes with stucco construction within each census division in 2015. Estimates are based on the residential energy consumption survey.*'

p_ci_stucco[,.(`Census Division` = division,
             `% Stucco Homes (95% CI)` =
               sprintf('%4.1f%% (%4.1f, %4.1f)',
                       100*p_stucco, 100*lwr, 100*upr))]%>%
  knitr::kable( align = 'r', caption = cap)
```


From this table, we can know that the division 'Mountain South' has the highest proportion, and 'East South Central' has the lowest proportion.


```{r q1a_figure1, fig.cap = cap}
library(ggplot2)
cap = 'Estimated percent of homes within each census division with major wall type of stucco.'

p_ci_stucco[, `:=`(Division = 
                     factor( as.character(division), 
                             as.character(division)))] %>%

  ggplot( aes( x = Division, y = 100*p_stucco) ) +
  geom_col( fill = 'navy' ) +
  geom_errorbar( aes( ymin = 100*lwr, ymax = 100*upr), 
                  col = 'darkslategrey') +
  theme_bw() +
  ylab('% Stucco Homes') +
  xlab('Census Division') +
  theme( axis.text.x = element_text(size = 8, angle = 90))

```


\pagebreak


### Part b

The average total electricity usage in kilowatt hours in each division is shown in the table 2 and figure 2 below. 
```{r q1b_table1}
cap = '*Average annual electricity utilization by Census Division in kwh/home.*'

# Pretty printing
pwc = function(x) format(round(x), big.mark = ',')

avg_ci_kwh[,
    .(`Census Division` = division,
    `Average Electricity Usage, kwh/home (95% CI)` = 
     sprintf('%s, (%s - %s)', 
             pwc(avg_kwh), pwc(lwr), pwc(upr) ))] %>%
  knitr::kable( align = 'r', caption = cap)

```


\pagebreak


```{r q1b_figure1, fig.cap = cap}
cap = 'Estimated average annual electricity usage in khw/home for each of 10 census divisions.'
avg_ci_kwh[, `:=`(Division = 
                     factor( as.character(division), 
                             as.character(division)))] %>%
  ggplot( aes(x = Division, y = avg_kwh) ) +
  geom_point() +
  geom_errorbar( aes(ymin = lwr, ymax = upr)) +
  coord_flip() +
  theme_bw() +
  ylab('kwh/home') +
  xlab('')

```


The average total electricity usage in kilowatt hours in each division for urban and rural is shown in the table 3 and figure 3 below.
 
 
```{r q1b_table2}
cap = '*Average electricity utilization in kwh per home for urban and rural areas witihin each census division.*'

avg_ci_urban[, .(`Census Division` = division,
                 ci= sprintf('%s, (%6s - %6s)', 
                             pwc(avg_kwh ), pwc(lwr), pwc(upr)),
                 Rurality = ifelse(urban=='Urban', 
                                   'Urban, kwh/home (95% CI)', 
                                   'Rural, kwh/home (95% CI)'))] %>%
  dcast(., `Census Division` ~ Rurality, value.var = 'ci') %>%
  .[order(-`Rural, kwh/home (95% CI)`)] %>%
  knitr::kable( align  = 'r', cap = cap)

```


\pagebreak


```{r q1b_figure2, fig.cap = cap}
cap = 'Estimated average annual electricity usage in khw/home for rural and urban areas in each of 10 census divisions.'

avg_ci_urban [,`:=`(Rurality = urban)] %>%
  ggplot( aes(x = division, y = avg_kwh, color = Rurality) ) +
  geom_point( position = position_dodge(.5) ) +
  geom_errorbar( aes(ymin = lwr, ymax = upr),
                 position = position_dodge(.5)
  ) +
  scale_color_manual( values = c('navy', 'darkred')[2:1]) +
  coord_flip() +
  theme_bw() +
  ylab('kwh/home') +
  xlab('')

```


### Part c

The disparity between urban and rural in internet access within each division is shown in the table 4 and figure 4 below.

The division 'Mountain South' has the largest disparity between urban and rural areas in terms of the proportion of homes with internet access.

```{r q1c_table1}
cap = "*Urban and rural disparity in internet access for the ten US Census Division in 2015.*"

p_ci_int[, .(division = division,
             urban=urban,
             ci= sprintf('%4.1f%% (%4.1f, %4.1f)',
                         p_it*100,lwr*100,upr*100)
             )] %>%
  dcast(., division ~ urban, value.var = 'ci') %>%
  merge(.,p_ci_diff, by='division',all=TRUE) %>%
  .[order(-p_diff)] %>%
  .[,.(`Census Division` = division,
       `Urban Internet Access, % (95% CI)`=Urban,
       `Rural Internet Access, % (95% CI)`=Rural,
       `Difference, % (95% CI)`=
         sprintf('%4.1f%% (%4.1f, %4.1f)',
                 p_diff*100,lwr*100,upr*100))] %>%
  knitr::kable( align  = 'r', cap = cap)

```


\pagebreak


```{r q1c_figure1, fig.cap = cap}
cap = 'Urban and rural disparity in internet access for the ten US Census Division in 2015'

p_ci_int [,`:=`(Rurality = urban)] %>%
  ggplot( aes(x = division, y = p_it*100, fill = Rurality) ) +
  geom_col( position = position_dodge() ) +
  geom_errorbar( aes(ymin = lwr*100, ymax = upr*100), 
                 position = position_dodge(),
                 col = 'slategrey') +
  theme_bw() + 
  xlab('') +
  ylab('% of homes with internet access') +
  ylim(c(0, 100)) +
  coord_flip() +
  scale_fill_manual(values = c('darkred', 'navy'))

```


### Part d

The average number of bedrooms for different type of housing units is shown in the table 5 and figure 5.

We can find that the type 'Single-family detached house' will have most bedrooms.

```{r  q1d_table1}
cap = '*Average numbers of bedrooms for different type of housing units*'

avg_ci_bed[,.(`Type of housing units` = type,
              `Average numbers of bedrooms, (95% CI)` =  
                sprintf('%s, (%s - %s)',round(avg_bed,3),
                        round(lwr,3), round(upr,3)))] %>%
  knitr::kable( align = 'r', caption = cap)

```



```{r q1d_figure1, fig.cap = cap}

cap = 'Average numbers of bedrooms for different type of housing units'

avg_ci_bed[, `:=`(Type= 
                     factor( as.character(type), 
                             as.character(type)))] %>%
  ggplot( aes(x = Type, y = avg_bed) ) +
  geom_point() +
  geom_errorbar( aes(ymin = lwr, ymax = upr)) +
  coord_flip() +
  theme_bw() +
  ylab('Average bedrooms') +
  xlab('')
```



\pagebreak



## Question 2

```{r q2_source, message = FALSE,include=FALSE}
source('./ps3_q2.R')
```


### Part a & b

The function in Part a is called 'mc_pval'.

I choose that  $\Sigma=I_{p \times p}$, $\Sigma$ is a $p \times p$ Identity matrix, and $\sigma = 10$.

The estimates of parameters of between the function in Part a is the same as the result of R function lm().

The estimates of parameters of X1 to X6 is shown in the talbe 6, torelance = 1e-3,

```{r q2_table1}
cap='*Compare estimates of parameters of X1 to X6 between the function in Part a and the R function lm(), tolerance=1e-3*'
col=c('Pval of Part_a','Pval of lm()','Difference')

cbind(head(pval_mc),head(pval_lm),
      head(round(pval_mc-pval_lm,3))) %>%
 knitr::kable( align = 'r', caption = cap,
               col.names = col,digits =4)
```




### Part c & d & e

The Monte Carlo estimates of the family wise error rate, the false discovery rate, the sensitivity, and the specificity of different types of adjusted p-values in multiple comparison are shown in the table 7 and figure 6.

When p-value is not adjusted, the family wise error rate is extremely large, and the false discovery rate is large also. But the adjusted p-values can fix this problem in some levels, and also improve the specificity.

```{r q2_table2}
cap='Monte Carlo estimates of the family wise error rate, the false discovery rate, the sensitivity, and the specificity of different types of adjusted p-values in multiple comparison'
col= c('','Family wise error rate', 'False discovery rate', 'Sensitivity', 'Specificity' )

row=c('Unadjusted','Bonferroni', 'Holm',
      'BH(Benjamini-Hochberg)', 'BY(Benjamini-Yekuteli)')

cbind(row,round(table,4))%>%
  knitr::kable( align = 'r', caption = cap, col.names = col)
```




```{r q2_figure1, fig.cap=cap}
cap='Monte Carlo estimates of the family wise error rate, the false discovery rate, the sensitivity, and the specificity of different types of adjusted p-values in multiple comparison'

group=c('Family wise error rate', 'False discovery rate', 'Sensitivity', 'Specificity' )
row=c('Unadjusted','Bonferroni', 'Holm','BH', 'BY')

data.frame(cbind(rep(row,4),as.vector(round(table,4)),
                 rep(group,each=5)))%>%
  ggplot(aes(x = X1,y=X2,group=X3,color=X3) ) +
  geom_line() +
  labs(x = 'Type of P-value', y = '',color = "Quantiles\n")

```



\pagebreak



## Question 3


```{r q3_source, message = FALSE,include=FALSE}
source('./ps3_q3.R')

```


### Part a

Computed by data.table, the table of univariate regression coefficients with groups is shown below.

```{r q3a_table}
cap='*The univariate regression coefficients with groups computed by data.table*'
col=c('Number of cylinders(Group)','Beta of Displacement','Beta of Gross horsepower','Beta of Weight')

beta_dt[,.(cyl,beta_cyl_disp,beta_cyl_hp,beta_cyl_wt)] %>%
  knitr::kable( align = 'r', caption = cap,digits=4,col.names = col)

```

### Part b

**beta_dt_fn** is the function for an arbitrary dependent, independent, and grouping varaibles.
The results computed by **beta_dt_fn** is shown below. It matches the Part a.

```{r q3b_table}
cap='*The univariate regression coefficients with groups computed by a function computing by data.table*'
col=c('Number of cylinders(Group)','Beta of Displacement','Beta of Gross horsepower','Beta of Weight')

beta_dt_fn(mtcars,'disp','mpg','cyl') %>%
  merge(.,beta_dt_fn(mtcars,'hp','mpg','cyl'),by='cyl') %>%
  merge(.,beta_dt_fn(mtcars,'wt','mpg','cyl'),by='cyl') %>%
  .[,.(cyl,beta_cyl_disp,beta_cyl_hp,beta_cyl_wt)] %>%
  knitr::kable( align = 'r', caption = cap,digits=4,col.names = col)
```

### Part c

Computed by dplyr summarize_at, the table of univariate regression coefficients with groups is shown below.

```{r q3c_talbe}
cap='*The univariate regression coefficients with groups computed by dplyr*'
col=c('Number of cylinders(Group)','Beta of Displacement','Beta of Gross horsepower','Beta of Weight')

beta_dplyr %>%
  select(cyl,beta_cyl_disp,beta_cyl_hp,beta_cyl_wt) %>%
  knitr::kable( align = 'r', caption = cap,digits=4,col.names = col)

```



\pagebreak


### Part d

**beta_dplyr_fn** is the function for an arbitrary dependent, independent, and grouping varaibles.
The results computed by **beta_dplyr_fn** is shown below. It matches the Part c.

```{r q3d_table}
cap='*The univariate regression coefficients with groups computed by a function computing by data.table*'
col=c('Number of cylinders(Group)','Beta of Displacement','Beta of Gross horsepower','Beta of Weight')

beta_dplyr_fn(mtcars,disp,mpg,cyl) %>%
  left_join(beta_dplyr_fn(mtcars,hp,mpg,cyl),by='cyl') %>%
  left_join(beta_dplyr_fn(mtcars,wt,mpg,cyl),by='cyl') %>%
  knitr::kable( align = 'r', caption = cap,digits=4,col.names = col)

```


